Enhancing Autonomy of Mobile Robots with Behavioral Tree using ROS2

### 2023-01-29 Paper/paper.tex
Updated abstract and title

\title{Behavioral Planning Approaches To Improve Autonomous Behaviour During
	Navigation for Mobile Robots Running ROS}

@@

This document is a model and instructions for \LaTeX.
This file define the components of your paper [title, text, heads, etc.]. 
*CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, or Math in Paper Title or Abstract.

>>>>

\title{Enhancing Autonomy of Mobile Robots with Behavioral Tree using ROS2}

@@

This paper proposes a behavioral planning approach to improve the autonomy of mobile robots using the Robot Operating System (ROS2). The study aims to address the issue of human intervention that is often required during the operation of autonomous mobile robots. The system includes a monitoring system, sensor data storage, and behavior tree design and implementation. The effectiveness of the approach was evaluated using the Gazebo simulator, with the behavior tree handling various scenarios such as sensor failures, collisions, unreachable goals, and low battery state. The simulation results showed a significant improvement in the robot's autonomy and resilience to failures. Additional validation is being performed through real-world experiments to confirm the results.
